Figure 1-Supplement 2e

### 2018-02-14 inst/cellular_localization_encode/cellular_localization_encode.Rmd
name change for cellular_localization_encode

stats <- fdata %>%
  group_by(`Biosample term name`, gene_id, gene_name, fraction) %>%
  filter(n() == 2) %>%
  summarize(
    n = n(),
    mean = mean(frac),
    sd_min = mean(frac) + sd(frac),
    sd_max = mean(frac) - sd(frac)
  )  %>%
  ungroup()
```

>>>>

stats <- fdata %>%
  group_by(`Biosample term name`, gene_id, gene_name, fraction) %>%
  filter(n() == 2) %>%
  summarize(
    n = n(),
    mean = mean(frac),
    sd_min = mean(frac) + sd(frac),
    sd_max = mean(frac) - sd(frac)
  )  %>%
  ungroup()

#prepare for plotting 
stats <- mutate(stats, gene_name = parse_factor(gene_name, levels = c("GAPDH", "MALAT1", "lncTAM34a")))
```
